### 2021-02-04 paper/rebuttal/rebuttal.tex

\tableofcontents
\listoffigures

\section{List of changes}

We have broken down the list of changes to the manuscript by referee.

\section{Point-by-point discussion}
All of the referees presented us with excellent, insightful comments and we feel that the changes implemented as a consequence have signiﬁcantly strengthened the manuscript. Here we offer further discussion, and introduce several results and figures to support certain arguments.

@@

\begin{itemize}
	\item Liu, Xin, Yong Liu, and Xiaoli Li. "Exploring the Context of Locations for Personalized Location Recommendations." IJCAI. 2016.
\item Feng, Shanshan, et al. "POI2Vec: geographical latent representation for predicting future visitors." AAAI. 2017.
\item Yao, Zijun, et al. "Representing Urban Functions through Zone Embedding with Human Mobility Patterns." IJCAI. 2018.
\item Cao, Hancheng, et al. "Habit2vec: Trajectory semantic embedding for living pattern recognition in population." IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
\end{itemize}

However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm. For example, the following references all propose word2vec-inspired embeddings of human mobility data:

Notably, the location embedding methodology in Liu et al (2016) (see Section 3.1) is essentially the same as the approach used in the submitted manuscript, and the work by Liu et al (2016) is well-known with over 100 citations.
}

\response{%
Thank you for pointing out the missing references. 
We have carefully read through all of your rec emended papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
}

\rcomment{
I found the specific use of the SGNS algorithm unmotivated. There are many ways to generate useful low-dimensional embeddings, so why is the SGNS method prioritized above others? This method is popular, but popularity alone is not sufficient justification and I see no theoretical reason why it should be the most appropriate method. For example, a key point in this manuscript is the fact that the the SGNS embeddings capture the flux between locations better than geographic distance. However, if this is such an important point, then why not simply learn a low-dimensional embedding approximation of the flux metric directly? such as SVD?
}

@@

In addition, we provided more explicit mathematical detail of word2vec in the new subsection entitled “word2vec and the gravity model”.

We believe that these details are sufficient in the main text of the manuscript, and refer readers to the Methods for a deeper explanation.
}

\rcomment{

The original SkipGram method expects environments of locations (originally words) with fixed length, however this is not explained in the manuscript nor in Methods or the SI.
Related question to the previous one. Let’s assume that the authors used fixed window lengths and, as mentioned in Methods Embedding section (and demonstrate in Fig.S4 - not referenced in Methods), that the windows size w=1 gives the best correlations in case of scientific mobility. This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w$>$1. Undersampling the ensemble of trajectories used for w=1 predictions might provide a fair way of comparing results of different window sizes.
}

\response{
\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
\todo{Maybe related to length of the trajectory @dakoda could you check this?
}
}

\rcomment{
The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored. E.g. to choose the ideal dimension for embedding one may sweep through a broad range of possible dimensions and not only explore three values as described in the SI (Fig.S4).
Their main observations in section “Embeddings provide functional distance between locations” is that “…our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.”. This is a great verification of their method but it is somewhat expected from an embedding, which is built on mobility trajectories between places, as compared to cases based on simply geographic distance.

}
\response{
\todo{ Can we test this? likes  yy's paper on optimal dimension of embedding }
Thank you for these comments. First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.  
}

\rcomment{
When datasets in the intro are explained, it should be mentioned that the detailed descriptions are in the Methods section.
}
\response{
Thank you. We have added a parenthetical to the introduction after stating the datasets, as follows:  \say{We embed trajectories from three massive datasets: U.S. passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).}
}
\rcomment{
Some minors comments
\begin{enumerate}
\item There is no reference to Fig.5e and f in the text.
\item Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.
\item Page 15, last row: double point in the end of sentence.
\item SI Page 2, S3: “. if” $\rightarrow$ “. If”
\end{enumerate}
}
\response{
Thank you, we have remedied these comments and have updates the manuscript accordingly, 
}

\rcomment{
SI Fig.S1c: Here the authors conclude that the proportions “decreased over time”. These proportions seem to be rather flat without strong decreasing trends. In any case, if the authors would like to indicate minor changes here, it would be helpful for the reader if a grid would be posted on the figure.
}
\response{

@@

\rcomment{
Finally, one cannot escape the fact that COVID changes our mobility patterns. Many groups have used mobile phone data to explore these changes. I wonder, how would the pre-covid embeddings apply to post-covid mobility? Once again, I am mindful that this would require access to such data, but I would not be surprised at all if the authors have access to such data—in which case this is remains an intriguing question.
}

\response{
This is an excellent idea, and one that we have been interesting in addressing as well. 
Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative. 
Publications are on a time lag, compared to actual events.
For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one. 
As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.

In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows. 
We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky (\href{https://nlp.stanford.edu/projects/histwords/}{[link]}), to align embeddings trained on different data in order to quantify the changes in global mobility. 
We look forward to approaching this, as well as other exciting projects in the future. 
}

\section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
In here, we would like to answer a question: why we use SGNS algorithms and is there any theoretical justification on that? This document details:
\begin{enumerate}
	\item Details on \textit{word2vec} algorithm
	\item An implicit bias in the negative sampling
	\item \textit{word2vec} and the gravity model

@@

In our paper, we employed a specific algorithm SGNS word embedding. However, it is well known that the negative sampling is a biased estimator~\autocite{Chia2010,Dyer2014} that optimizes a distinct model  from {\it word2vec}.

Negative sampling trains {\it word2vec} using a binary classification task as follows.
A center-context word pair $(i,j)$ is sampled from the given data as a positive pair, and $k$ negative pairs $(i,\ell)$ are sampled from a noise distribution $p_0(\ell)=P^\gamma(\ell)$. ($P(j)$ is the fraction of $j$ in the data, and $\gamma>0$ is a parameter).
Then, given a center-context word pair $(i,j)$, the model predicts whether it is a positive or negative sample using sigmoid function:
\begin{align}
	\label{eq:sigmoid}
	\frac{1}{1 + \exp\left( - \bm{u}_j \cdot \bm{v}_i \right)}.
\end{align}

This procedure does not guarantee that the embedding optimally converges to the original conditional probability eq.\ref{eq:cond_prob_w2v}, even when increasing the training samples and iterations~\autocite{Chia2010,Dyer2014} in the fact that negative sampling has implicit bias.
This problem is addressed by the noise contrastive estimation (NCE) \autocite{Chia2010}, which fits a probability model in the form:
\begin{align}
	\label{eq:nce}
	f(x) / \sum_{x'} f(x'),
\end{align}
where $f(x)$ is the unnormalized probability for an instance $x$. As in negative sampling, NCE fits the model based on a binary classification task, with positive and negative samples randomly drawn from the given data and a noise distribution $p_0$, respectively, using a bias-corrected sigmoid function:
\begin{align}
	\label{eq:sigmoid2}
	\frac{1}{1 + \exp\left( -f(x) + \log p_0(x) \right)}.
\end{align}

Rewriting the sigmoid function for the negative sampling (Eq.~\eqref{eq:sigmoid}) in form of the bias-corrected sigmoid function yields
\begin{align}
	\label{eq:sigmoid3}
	\frac{1}{1 + \exp\left[ - \tilde f(x) + \log p_0(x)  \right]},
\end{align}
where we have defined
\begin{align}
	\label{eq:unnormalized}
	\tilde f(x) = f(x) p_0(x).
\end{align}
So, the model with the negative sampling optimize $\tilde f(x)$, not $f(x)$. In case of the {\it word2vec}, the instance is the dot similarity $x=\bm{u}_i \cdot \bm{v}_j$,  $f(x)=\exp(x)$, and $p_0(j)=P^\gamma(j)$, and the SGNS word2vec actually optimize the following conditional probability:
\begin{align}
	P\left(j \given i \right):= \frac{P^\gamma (j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{\widetilde{Z_i}},
	\label{eq:real_cond}
\end{align}
where $\widetilde {Z_i}=\sum_{j' \in \mathcal{A}} P^\gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.

\subsection{\textit{word2vec} and the gravity model}

Taking into an implicit bias in the negative sampling  and set $w=1$, the \textit{word2vec} predict the flow with
\begin{align}
\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P^\gamma (j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:prob_w2v_ng0}
\end{align}
where  $\widetilde{Z_i}=\sum_{j' \in \mathcal{A}} P^ \gamma (j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.

Parameter $\gamma=1$ is a special choice that ensures that, when the embedding dimension is sufficiently large, there exists optimial in-vectors and out-vectors such that $\bm{u}_i = \bm{v}_i$ \autocite{levy2014neural}.
Setting $\gamma = 1$ and substituting $\bm{u}_i = \bm{v}_j$ into Eq.~\eqref{eq:prob_w2v_ng0}, the flow predicted by {\it word2vec} is given by
\begin{align}
	\hat{T_{ij}}= P(i) P(j\given i) = \frac{P(i)P(j)\exp(\bm{v}_j \cdot \bm{v}_{i})}{Z_i}. \label{eq:flow_w2v_ng1}
\end{align}

The flow $\hat{T_{ij}}$ is symmetric (\ie $\hat{T_{ij}}=\hat{T_{ji}}$) because {\it word2vec} neglects whether the context $j$ appears before or after the center $i$ in the trajectory -- the mechanism of skip-gram.
If we swap $i$ and $j$ in Eq.~\eqref{eq:flow_w2v_ng1}, the numerator remains the same but the denominator can be different.
Therefore, to ensure $T_{ij} = T_{ji}$, the denominator $Z_i$ should be a constant.

Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
\begin{align}
	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
\end{align}
where $C$ is a positive constant.

In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.

\subsection{Some concerns on this section??}
\todo{
Why cosine similarity is better? In-vector and out-vectors are different in our result}

\section{Performance of \textit{word2vec} compared with baselines}
\subsection{The method we have used for the test}
\todo{list methods in here}
\subsection{Result}
\todo{report the results and say our results are better
Why SGD has a lower performance and SGNS yield better performance
power of stochastic gradient descent algorithm \autocite{smith2020generalization}}

\clearpage
%
% Figure - Distance metric performance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=0.9\textwidth]{\figdir/Descriptive/distance_metric_performance.pdf}
		\mycaption
		{Comparison a correlation with flux across various baselines}
		{
		Cosine distance between embedding vectors explains more flux in scientific mobility than geographic distance, baselines.
		The correlation, or amount of flux explained by the embedding distance across distance metrics and other experimental parameters. 
		All correlations are significant at $p < 0.0001$). 
		Distance metrics are ordered, from top to bottom, by the highest correlation ($r^{2}$). 
		The asterisk denotes the top-performing distance metric for every case. 
		All distance metrics explain more of the flux than does geographic distance.
		The cosine distance between embedding vectors explains more flux than all other distance metrics. 
		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
		Generally, ``All'' explains more of the flux, however there is little difference between definitions of mobility.
		All distance metrics tend to explain more of the flux when describing all or domestic (same-country) mobility.	
		}
	\label{fig:supp:distancemetrics}
\end{figure}

\clearpage
\begin{figure}[p!]
	\centering
	\includegraphics[width=0.85\textwidth]{\figdir/Descriptive/distance_prediction_performance_rmse.pdf}
		\mycaption
		{Comparison of prediction power across various baselines}
		{Using cosine distance between embedding vectors as input to the gravity model results in better predictions of scientific mobility compared to geographic distance, baselines.
		Shown is the Root Mean Squared Error (RMSE), or the accuracy of predictions made with the gravity model of mobility using the embedding distance and other experimental parameters.
		The RMSE is shown using both the exponential and power-law forms of the gravity model. 
		For each distance metric and set of parameters, the RMSE is shown for 
		Distance metrics are ordered, from top to bottom, by the lowest RMSE, where a lower error indicates better predictions. 
		The asterisk denotes the best-performing distance metric for every case. 
		The x-axis differentiates between three strategies for defining the organization population used to calculate the flux. 
		``All'' means that population is defined as the average yearly number of unique mobile and non-mobile scholars who published with the organizations' affiliation;
		population is defined in the same way for ``mobile-only'', except only using unique mobile researchers;
		``Raw frequency'' means that organization populations are defined as their frequency across all the trajectories, similar to word frequency in language embedding. 
		Generally, ``All'' results in better prediction.
		}
	\label{fig:supp:distancermse}
\end{figure}

### 2021-02-04 paper/rebuttal/rebuttal.tex

\documentclass[12pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{pslatex}
\usepackage{color}
\usepackage{bm}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\definecolor{orange}{RGB}{230, 81, 0}
\definecolor{purple}{RGB}{170, 0, 255}
\definecolor{mygreen}{RGB}{76, 175, 80}
\usepackage{framed}
\definecolor{shadecolor}{RGB}{210, 210, 210}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{newtxmath}
\DeclareMathAlphabet{\mathpzc}{T1}{pzc}{m}{it}
\def\given{\mid}
\usepackage{bm}
\def\tnull{{\text{null}}}
\def\vec#1{{\bm #1}}
\def\mat#1{\mathbf{#1}}

% abbreviations
\def\etal{\emph{et~al}.\ }
\def\eg{e.g.,~} 
\def\ie{i.e.,~}
\def\cf{cf.\ }
\def\viz{viz.\ }
\def\vs{vs.\ }

\usepackage{hyperref}

\usepackage[style=nature,
					backend=biber,
					sortcites=true,
					autocite=superscript
]{biblatex}

\AtEveryBibitem{%
 \clearfield{url}%
   \clearfield{month}%
 \clearfield{issn}%
 \clearfield{doi}%%
}

\addbibresource{rebuttal.bib}

@@

\tableofcontents
\listoffigures

\section{List of changes}

We have broken down the list of changes to the manuscript by referee.

\begin{itemize} 
\item \textbf{Referee 1} 
     \begin{itemize} 
        \item blah
        \item blah
     \end{itemize}
\item \textbf{Referee 2} 
     \begin{itemize} 
        \item blah
        \item blah
     \end{itemize}
\item \textbf{Referee 3} 
     \begin{itemize} 
        \item blah
        \item blah
     \end{itemize}
 \item \textbf{Referee 4} 
     \begin{itemize} 
        \item blah
        \item blah
     \end{itemize}
\end{itemize}

@@

Taken altogether, the {\it word2vec} model with the negative sampling predicts a flow in the same form as in the gravity model:
\begin{align}
	\hat{T_{ij}}=  C P(i) P(j)  \exp(\bm{v}_j \cdot \bm{v}_{i}), \label{eq:flow_w2v_ng0}
\end{align}
where $C$ is a positive constant.

In other words, \emph{word2vec with the negative sampling is a gravity model}, with the mass given by the location's frequency $P(i)$, and the distance measured by their dot similarities.
While the gravity model generates the flow from the given mass and locations, {\it word2vec} finds the mass and locations that best explain the given trajectories.
Therefore, the embedding distance is inherently tied to the flow, and hence, has greater predictive power than the geographic distance.

\subsection{Some concerns on this section??}
\todo{
Why cosine similarity is better? In-vector and out-vectors are different in our result}

\section{Performance of \textit{word2vec} compared with baselines}
\subsection{The method we have used for the test}
We list baselines that we have used for the validation. For embedding baselines, we set $d=300$ for the pair comparison.\\\\
\textbf{SVD-based embedding baselines}
\begin{itemize}
    \item Truncated SVD on the flow matrix
	\item  Laplacian eigenmap
	\item Levy's word2vec
\end{itemize}
\textbf{Network-based baselines}
\begin{itemize}
    \item Personalized Page Rank
\end{itemize}
\textbf{Geographical baselines}

\subsection{Result}
\todo{report the results and say our results are better
Why SGD has a lower performance and SGNS yield better performance
power of stochastic gradient descent algorithm \autocite{smith2020generalization}}
also, compare the speed?

### 2021-02-04 paper/rebuttal/rebuttal.tex

\addbibresource{rebuttal.bib}

\DeclareUnicodeCharacter{FB01}{fi}
\usepackage{dirtytalk}

\def\figdir{../Figs}

\usepackage[most]{tcolorbox}
\newcommand{\sada}[1]{{\leavevmode\color{orange}[SK: #1]}}
\newcommand{\sadaadded}[1]{{\leavevmode\color{orange}{#1}}}
\newcommand{\todo}[1]{{\leavevmode\color{orange}[TODO: #1]}}
\newcommand{\add}[1]{{\leavevmode\color{blue}#1}}
\newcommand{\del}[1]{{\leavevmode\color{red}\sout{#1}}}
\newcommand{\response}[1]{{\noindent #1}}
%\newcommand{\rcomment}[1]{{\bigskip\begin{snugshade}\begin{quotation}\noindent #1 \end{quotation}\end{snugshade} }}
\newcommand{\rcomment}[1]{%
\vspace{10pt}
\begin{tcolorbox}[colback=black!3,colframe=white!45!black, left=0pt, right=0pt, top=0pt, bottom=0pt, arc=0pt,outer arc=0pt, grow to left by=-0.5cm,grow to right by=-0.5cm]
#1
\end{tcolorbox}
}
\newcommand{\correction}[2]{{\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}
%\newcommand{\correction}[2]{{\bigskip\begin{quotation}\noindent {#1}{\it #2} \end{quotation} }}

@@

\begin{itemize}
	\item Liu, Xin, Yong Liu, and Xiaoli Li. "Exploring the Context of Locations for Personalized Location Recommendations." IJCAI. 2016.
\item Feng, Shanshan, et al. "POI2Vec: geographical latent representation for predicting future visitors." AAAI. 2017.
\item Yao, Zijun, et al. "Representing Urban Functions through Zone Embedding with Human Mobility Patterns." IJCAI. 2018.
\item Cao, Hancheng, et al. "Habit2vec: Trajectory semantic embedding for living pattern recognition in population." IEEE Transactions on Mobile Computing 19.5 (2019): 1096-1108.
\end{itemize}

However, the novelty of this work is quite narrow, as there are several prior works that develop trajectory-based embeddings of human mobility based on the word2vec algorithm. For example, the following references all propose word2vec-inspired embeddings of human mobility data:

Notably, the location embedding methodology in Liu et al (2016) (see Section 3.1) is essentially the same as the approach used in the submitted manuscript, and the work by Liu et al (2016) is well-known with over 100 citations.
}

\response{Thank you for pointing out the missing references. 
We have carefully read through all of your rec emended papers, learning a lot in the process, and have incorporated them into our manuscript's introduction.
}

@@

\rcomment{
I found the specific use of the SGNS algorithm unmotivated. There are many ways to generate useful low-dimensional embeddings, so why is the SGNS method prioritized above others? This method is popular, but popularity alone is not sufficient justification and I see no theoretical reason why it should be the most appropriate method. For example, a key point in this manuscript is the fact that the the SGNS embeddings capture the flux between locations better than geographic distance. However, if this is such an important point, then why not simply learn a low-dimensional embedding approximation of the flux metric directly? such as SVD?
}

\response{Thank you for the suggestion! 
We split our response into two subsections concerning the theoretical justification, on one hand, and the comparison to simpler baselines, on the other. 
}

\rcomment{%
The methodology has potential limitations in terms of reproducibility and robustness, which should be addressed. This is no specific fault of the authors, but both the SGNS/word2vec algorithm and the UMAP algorithm are inherently stochastic. This means that these approaches involve inherent randomness, and for researchers to replicate the exact effect seen in this manuscript, one would need to ensure the exact same random seeds etc. were used. In my view, this is a serious limitation, especially given that the UMAP results and learned embeddings are reified and treated as first-class objects of scientific study. 
}

\response{Thank you for this comment. While robustness is a general concern for these methods, we found that their application to our datasets were in fact quite robust, and observed no evidence that findings were the result of methodological artefacts. This is confirmed in extra work done in response to these reviews.

\noindent We re-ran all of our results using different starting seeds and found all results were qualitatively similar, and almost quantitatively identical. 
In addition, we expanded the set of experimental parameters, training 18 different embeddings with different dimensions, window sizes, and now, $\gamma$. 
We found that while performance varies across each combination of parameters, the main results remain qualitatively similar. 
While we can run more combinations of parameters, and more iterations of \textit{word2vec}, we see no evidence that results will drastically vary.

\noindent We believe that the ratio of the number of organizations represented in our dataset to the total number of mobility trajectories makes our results especially robust. 
Only about 8,661 organizations are represented across over three million career trajectories of scientists, such that nearly every organization appears enough times, and in enough contexts, to produce a robust vector representation. 
However, this may not hold true for all problem domains—for example, natural language includes many millions of tokens, many of which will occur only a few times, allowing stochasticity to have a much stronger effect on the final representation. 
Heeding this as a general concern, we have added the following sentence to our limitations paragraph in our conclusion:

\noindent “We however, note that all results shown here are robust to this stochasticity, likely emerging from the limited "vocabulary" of scientific mobility, airports, and accommodations (several thousand) and the massive datasets used (several million trajectories). Applications of word2vec to problem domains where the ratio of the vocabulary to data is smaller, however, should take caution to ensure that findings are not the result of random artifacts.”

@@

We have also provided detail about how confidence intervals were calculated in relevant figure captions. 
For example, we state in figure 2's caption that \say{\textit{99\% confidence intervals are plotted for the mean flux in each bin based on a normal distribution.}}, which should give readers enough information to reproduce the confidence intervals following their standard definition. 
Other confidence intervals, such as intervals for the loess regression line in figure 6, are calculated using the smoothing functions in the \texttt{ggplot2} package of R, and refer readers to the relevant documentation. 
}

\rcomment{%
F. Suggested improvements:
References and discussion of prior work using word2vec-style embeddings of mobility data.
Additional experiments using alternative embedding methods, especially an SVD-based embedding method, as well as robustness/reproducibility studies across different runs of the SGNS would be essential to strengthen the paper.
In addition, some additional results demonstrating how the embeddings provide novel scientific insight, rather than just recapitulating known structures, would be essential to make this work above-the-bar for a high-impact publication such as Nature.

}

\response{We believe that the mathematical breakthroughs made since our first submission improve the manuscript and extend its contribution and demonstrates novel scientific insight, and justifies the use of word2vec towards mobility data. By adding this, and addressing your other points (above), we believe that the revised manuscript sufficiently remedies your concerns.

@@

}

\bigskip
\response{In summary, we have updated the manuscript by providing the appropriate context in the literature, clarifying the limitations of our study, and extending our approach to incorporate delays in contact tracing. We deeply appreciate the Referee's careful reading of the paper and their constructive comments. 
%We hope that have correctly addressed the Referee's concerns and comments.
}

@@

The original SkipGram method expects environments of locations (originally words) with fixed length, however this is not explained in the manuscript nor in Methods or the SI.
Related question to the previous one. Let’s assume that the authors used fixed window lengths and, as mentioned in Methods Embedding section (and demonstrate in Fig.S4 - not referenced in Methods), that the windows size w=1 gives the best correlations in case of scientific mobility. This might be true in absolute terms but it is an unfair comparison to larger window sizes, as there are way more short trajectories in the data than longer ones (see Fig.S3), thus the flux prediction of w=1 is based on a way larger sample than for w$>$1. Undersampling the ensemble of trajectories used for w=1 predictions might provide a fair way of comparing results of different window sizes.
}

\response{\todo{need to finish this. Honestly, I have no idea what they are saying about the window length}
\todo{Maybe related to length of the trajectory @dakoda could you check this?
}
}

\rcomment{
The other very important parameter of the SkipGram method is the embedding dimension, which is explained in the Methods but it is not explored. E.g. to choose the ideal dimension for embedding one may sweep through a broad range of possible dimensions and not only explore three values as described in the SI (Fig.S4).
Their main observations in section “Embeddings provide functional distance between locations” is that “…our results demonstrate that, consistently, the embedding distance better captures patterns of actual mobility than does the geographic distance.”. This is a great verification of their method but it is somewhat expected from an embedding, which is built on mobility trajectories between places, as compared to cases based on simply geographic distance.

}
\response{\todo{ Can we test this? likes  yy's paper on optimal dimension of embedding }
Thank you for these comments. First, we added a line to the methods section detailing the \textit{word2vec} we used, and noting that these achieved the bst performance: \say{\textit{For main results regarding scientific mobility, we used $d=300$ and $w=1$, which were the parameters that best explained the flux between locations, though results were robust across different settings (Fig....)}}.  
}

\rcomment{
When datasets in the intro are explained, it should be mentioned that the detailed descriptions are in the Methods section.
}
\response{Thank you. We have added a parenthetical to the introduction after stating the datasets, as follows:  \say{We embed trajectories from three massive datasets: U.S. passenger flight itinerary records, Korean accommodation reservations, and a dataset of scientists' career mobility between organizations captured in bibliometric records (Detailed descriptions are available in the Methods).}
}
\rcomment{
Some minors comments
\begin{enumerate}
\item There is no reference to Fig.5e and f in the text.
\item Second paragraph on page 10: the authors discuss Fig.6 here but missed to refer the figure.
\item Page 15, last row: double point in the end of sentence.
\item SI Page 2, S3: “. if” $\rightarrow$ “. If”
\end{enumerate}
}
\response{Thank you, we have remedied these comments and have updates the manuscript accordingly, 
}

\rcomment{
SI Fig.S1c: Here the authors conclude that the proportions “decreased over time”. These proportions seem to be rather flat without strong decreasing trends. In any case, if the authors would like to indicate minor changes here, it would be helpful for the reader if a grid would be posted on the figure.
}
\response{Thank you, we agree that the trend is flat, rather than decreasing. We have adjusted the text accordingly, and also added a grid to the figure so that it can be more easily read.

@@

}

\rcomment{
SI Fig.S3: Posted numerical values on the figures and the values described in the caption do not match.
}
\response{Thank you for pointing out this oversight. The caption values have been updated. 
}

\rcomment{SI Fig.S6: Please indicate what is RMSE in the caption. The authors defined it in the main text but the SI should be self consistent too.
}
\response{We have added the line “RMSE is the root-mean-squared error between the actual and predicted values.” to Fig. S6 as well as all other SI figures that make use of the same visualization.
}

\rcomment{SI Fig.S7: The authors state that “The gravity model with the exponential decay function outperforms that with a power-decay function.” - this does not seem to be true for the “International” case. Please specify this in the caption.
}

\response{We have updated the relevant line of the caption to read as follows: 
“The gravity model with the exponential decay function slightly outperforms that with a power-decay function except in the case of international-only mobility, for which power-decay performs slightly better.”
}

@@

\subsection{Response to Referee 3}

\rcomment{The analysis does not compare embeddings, which would not be a problem if they were making
an inference other than we can embed micro-mobility to trace macro-mobility. They use an
efficient (Google engineers developed it), single-layer embedding from 2013, which produces
linear associations. But the paper doesn’t take advantage of the revolution in deep neural
network models that now produce powerful, nonlinear and noncontiguous (e.g., using the
attention architecture) models that now dominate analysis of language, and are making very
power inroads in machine vision. To be clear, deeper models require much data and computational power to tune—they are an engineering feat—but if developed in these settings, they would likely dramatically improve the prediction of flux. They take into account directionality (e.g., a person moving from one opportunity to another) and would independently capture people how people distinctly move up and down the hierarchy or from place to place (e.g., a in bi-directional model like BERT). A lack of discussion or demonstration of which model works best--and the unfounded inference that direction does not matter felt weak without a demonstration that they would not have worked better. They did and do work much better for language models and for image generation...why would they not work for analysis of human mobility? (I’m sure they would, but this would time and independent development.)
}

\response{Thank you for this insightful comment. 
We think that there is a great deal of potential in methods like BERT for representing mobility data.
What initially drew us to \textit{word2vec}, however, was its simplicity, its ubiquity, and its mathematical tractability (at least compared to other, more sophisticated approaches). 
This last attribute proved very useful, as in exploring the mathematical properties of the model, we discovered a deep connection between \textit{word2vec} and the Gravity Model of Mobility, which explains why it learns such effective gravity-like relationships between entities. 
We believe hat this new discovery, not included in the manuscript (and illustrated below), justify our use of \textit{word2vec} here. 
We agree that the revolution in neural embeddings offers great promise in mobility and look forward to reading and also working on these future studies; however we argue that our contribution is most well founded, and best serves the scientific community, by working with simpler and more established models, especially concerning the mathematical link we uncovered. 
To highlight the importance of altenrative models, however, we add the following line to our conclusion: \say{\textit{Future studies may also consider bi-directional embeddings, such as BERT~\autocite{devlin2018bert}, to incorporate directionality. }}.

@@

\rcomment{
P6Para3: “For THEIR purpose…”
}

\response{Thank you, we have corrected this mistake. 
}

\rcomment{
P8Para1: “by explicitly the relative importance of different level of the hierarchy with a scaling parameter r ” which is never described or explained. Considering it was derived by the authors in a very recent paper, no one will know what it is.
}

\response{Thank you, we have edited the text to read as “We quantify the relative importance of geography (by region), and language (by the most widely-spoken language of each country) using the element-centric clustering similarity, a method that can compare hierarchical clustering and disjoint clustering (geography, language...) at the different level of hierarchy by explicitly adjusting a scaling parameter $r$, acting like a zooming lens”
}

@@

\response{Thank you for this idea!
We believe that this is an interesting topic and we hope to investigate it in the future. 
In your particular example, an embedding distance trained using sequences of co-authorship on the same paper might be better to capture the \textit{collaborative} distance between institutions. 
Then, using that distance, one could measure the "embedding distance" spanned by all authors in the byline, and relate this to questions impact to determine whether (a)typical collaborations relate to impact. 
This is certainly a topic that is in our mind for future study. 
In the case of scientific mobility, we might also consider the "embedding distance" spanned by an individual's career, and relate this to their demographics and scientific impact.

However, while these topics are exciting, we believe that that they fall outside the scope of the current manuscript, especially given the discoveries we made concerning a fundamental connection between the gravity law of mobility and \textit{word2vec}.
}

\rcomment{
Finally, one cannot escape the fact that COVID changes our mobility patterns. Many groups have used mobile phone data to explore these changes. I wonder, how would the pre-covid embeddings apply to post-covid mobility? Once again, I am mindful that this would require access to such data, but I would not be surprised at all if the authors have access to such data—in which case this is remains an intriguing question.
}

\response{This is an excellent idea, and one that we have been interesting in addressing as well. 
Unfortunately, however, we do not have access to such data, at least not in large enough quantiaties to be representative. 
Publications are on a time lag, compared to actual events.
For example, a researcher may write a paper while studying at university $A$, but then before the final paper is published, move to university $B$, so while they now have a $B$ affiliation, in our data all we see is the $A$ one. 
As such, we would not necessarily expect to  see the impact of COVID on bibliometric data until later in 2021 or early 2022, when researchers have had the chance to publich with their new institution.
We also not that some activity will, of course, be visible, especially given the number of researchers rapidly publishing on the subject of COVID-19, however we consider this to be an unrepresentative sample, given that it is concentrated in a few disciplines.

@@

In the future, however, we hope to have access to a fully-representative sample of mobility data to study the effects of COVID-19 on global scientific labor flows. 
We can use techniqeus developed by other researchers, such as those used by Hamilton, Leskovec, \& Jurafsky (\href{https://nlp.stanford.edu/projects/histwords/}{[link]}), to align embeddings trained on different data in order to quantify the changes in global mobility. 
We look forward to approaching this, as well as other exciting projects in the future. 
}

\section{Theoretical justification of \textit{word2vec} and the Gravity Model} 
In here, we would like to answer a question: why we use SGNS algorithms and is there any theoretical justification on that? This document details:
\begin{enumerate}
	\item Details on \textit{word2vec} algorithm
	\item An implicit bias in the negative sampling
	\item \textit{word2vec} and the gravity model

\end{enumerate}

\subsection{Details on \textit{word2vec} algorithm}
We used standard skip-gram negative sampling word embedding, commonly known as \textit{word2vec}~\autocite{mikolov2013word2vec}.
Suppose a trajectory, denoted by ($a_{1}, a_{2}, \ldots, a_{T}$), where $a_{t}$ is the $t$th location in the trajectory. A location, $a_{t}$, is considered to have context locations, $a_{t-w}, \ldots, a_{t-1}, a_{t+1},\ldots, a_{t+w}$, that appear in the window surrounding $a_t$ up to a time lag of $w$, where $w$ is the window size parameter truncated at $t - w \geq 0$ and $t + w \leq T$. Then, the model learns probability $p(a_{t + \tau} \vert a_{t})$, where $-w\leq \tau\leq w$ and $\tau \neq 0$,  by maximizing its log likelihood given by
%
% MAIN W2V Equation
%
\begin{equation}
	\frac{1}{T}\sum_{t = 1}^{T} \sum_{-w \leq \tau \leq w, \tau \neq 0} \log p(a_{t + \tau} \vert a_{t}),
\end{equation}
where,
